\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=0.72in]{geometry}
\usepackage{array,tabularx}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\definecolor{accent}{HTML}{111111}
\definecolor{textgray}{HTML}{444444}

\titleformat{\section}
  {\large\bfseries\scshape\color{accent}}
  {}{0em}{}
  [\vspace{0.18em}\titlerule]
\titlespacing*{\section}{0pt}{0.75em}{0.45em}

\newcommand{\entry}[4]{%
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}\\[-0.35em]
}

\newcommand{\cvitem}[1]{\item \small #1}
\newcommand{\contactsep}{\hspace{0.7em}{\color{textgray}|}\hspace{0.7em}}

\begin{document}

{\centering
    {\LARGE\bfseries Chuyao Fu}\\[0.45em]
    {\small
    \faEnvelope\ \href{mailto:12310306@mail.sustech.edu.cn}{12310306@mail.sustech.edu.cn}
    \contactsep
    \faGithub\ \href{https://github.com/ChuyaoZellFu}{github.com/ChuyaoZellFu}
    \contactsep
    \faGlobe\ \href{https://chuyaozellfu.github.io/}{chuyaozellfu.github.io}
    \contactsep
    \faPhone\ +86 153 4733 9211
    }\\[0.3em]
    {\small \color{textgray}Shenzhen, China \;\; / \;\; Undergraduate researcher in embodied AI, world models, and multimodal learning}
\par}

\section*{Education}
\entry{Southern University of Science and Technology}{Sep. 2023 -- Jun. 2027 (expected)}{B.Eng. in Electronic Information Engineering}{GPA: 3.90/4.00 \;\; Rank: 3/46}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{\textbf{Selected Coursework:} Data Structures and Algorithm Analysis, Probability and Statistics, Machine Learning, Robotic Motion and Control, Digital Signal Processing, Signals and Systems, Analog Circuits, Digital Circuits}
\end{itemize}

\section*{Publications}

\noindent
\textbf{ProDrive:} Proactive Planning for Autonomous Driving via Ego-Environment Co-Evolution \\
\textbf{Chuyao Fu}, S. Gan, Z. Ouyang, Y. Rui, Z. Qian, X. Chi, S. Han, J. Wang, Z. Hong \\
\textit{CVPR 2026 GigaBrain Challenge Workshop (Poster)}

\vspace{0.9em}

\noindent

\textbf{Token-World:} Native Latent Dynamic World Model for Vision-Language-Action Models\\
\textbf{Chuyao Fu}, X. Chi, H. Li, Y. Rui, Z. Qian, Y.-K. Wang, X. Zhang, Y. Lou, H. Cheng, Y. Guo, S. Han, S. Zhang.\\
\textit{ECCV 2026 (under review)}

\vspace{0.9em}

\noindent
\textbf{EchoArena:} Mutual Benchmarking of World Models and VLA Policies\\
Y.-K. Wang, K. Zhang, X. Chi, T. Chen, S. Huang, \textbf{Chuyao Fu}, T. Guo, P. Jia, Y. Qin, K. Ge, S. Qian, W. Mi, Z. Qian, J. Li, Q. Wuwu, S. Zhang\\
\textit{ECCV 2026 (under review)}

\vspace{0.9em}

\noindent
\textbf{FORCE:} Efficient VLA Reinforcement Fine-Tuning via Value-Calibrated Warm-up and Self-Distillation\\ S. Zhang, Y. Lou, H. Cheng, Y. Guo, \textbf{Chuyao Fu}, Y. Lyu, X. Zhang, H. Li, P. Wang, Z. Wang, S. Zhang\\
\textit{ICML 2026 (under review)}

\vspace{0.9em}

\noindent
\textbf{Predicting What Matters:} Robust Generalist Robot Policy Learning via Future Semantic Mask\\
Y. Lou, X. Chi, X. Zhang, Z. Qian, C. Li, R. Zhang, Y. Lyu, G. Song, \textbf{Chuyao Fu}, H. Xu, P. Wang, S. Zhang\\
\textit{ICML 2026 (under review)}

\section*{Research Experience}

\entry{Robotics and Computer Vision Lab, Southern University of Science and Technology}{Sep. 2024 -- Present}{Undergraduate Researcher}{Supervisor: Prof. Hong Zhang}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{\textbf{Topics:} Social Navigation and Autonomous Driving.}
  \begin{itemize}[leftmargin=1.4em, topsep=0.15em, itemsep=0.12em]
    \item Contributed to \textbf{TPT-Bench} data collection for social navigation and gained hands-on experience with ROS bag processing, multisensor synchronization, and data preprocessing (\textit{paper under review at IJRR}).
    \item Independently proposed \textbf{ProDrive}, a proactive autonomous driving framework that jointly trains a driving planner and a BEV world model via \emph{ego-environment co-evolution}.
    \item Demonstrated stronger performance than several prior world-model-based driving frameworks on NAVSIM v1, improving both navigation efficiency and safety.
    \item \textbf{First author}; led method design, experiments, and manuscript preparation. Accepted by the \textit{CVPR 2026 GigaBrain Challenge Workshop}.
  \end{itemize}
\end{itemize}

\entry{HMI Lab, School of Computer Science, Peking University}{Jun. 2025 -- Present}{Undergraduate Researcher}{Supervisor: Prof. Shanghang Zhang}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{\textbf{Topic:} Vision-Language-Action Models, World Models, and Latent-Space Simulation.}
  \begin{itemize}[leftmargin=1.4em, topsep=0.15em, itemsep=0.12em]
    \item Proposed \textbf{Token-World}, a latent world model for VLA systems that predicts future visual tokens directly in token space, eliminating intermediate RGB reconstruction.
    \item Designed a spatio-temporal multimodal Transformer with GRU-enhanced temporal modeling for action-conditioned long-horizon prediction.
    \item Combined flow matching with diffusion forcing to improve rollout stability and reduce autoregressive error accumulation.
    \item Developed a latent reward model and imagined rollout evaluation pipeline for policy assessment in latent space.
    \item Outperformed strong RGB-based world-model baselines on RoboTwin in rollout error, semantic similarity, and inference speed.
    \item \textbf{First author}; led method design, experiments, and manuscript preparation. Submitted to \textit{ECCV 2026} (under review).
  \end{itemize}
\end{itemize}

\entry{Beijing Academy of Artificial Intelligence}{Jun. 2025 -- Nov. 2025}{Research Intern, Embodied Multimodal Large Models Research Center}{Mentor: Xiaojie Zhang}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{\textbf{Topic:} Reinforcement Learning for Vision-Language-Action Models and Flow-Based Robot Policies.}
  \begin{itemize}[leftmargin=1.4em, topsep=0.15em, itemsep=0.12em]
    \item Reproduced representative VLA-RL and robot policy post-training frameworks, including \textit{RLinf}, \textit{SimpleVLA-RL}, \textit{RL4VLA}, and \textit{DSRL}.
    \item Investigated reinforcement learning objectives for flow-based robot policies, focusing on training stability, inference efficiency, and compatibility with modern VLA backbones.
    \item Contributed to the early development of the \textbf{FORCE} project through idea exploration, baseline execution, and result organization.
    \item Supported manuscript preparation, including paper polishing and figure refinement; co-authored an \textit{ICML 2026} submission (under review).
  \end{itemize}
\end{itemize}

\section*{Work Experience}
\entry{XtalPi}{Jan. 2026 -- Present}{Research Intern, Future Chemistry Department}{Shenzhen}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{\textbf{Topic:} Humanoid Robots for Laboratory Automation; Vision-Language-Action Policy Learning and Deployment.}
  \begin{itemize}[leftmargin=1.4em, topsep=0.15em, itemsep=0.12em]
    \item Trained VLA policies for humanoid robot manipulation in laboratory environments, focusing on tool use and structured object interaction.
    \item Deployed policies on real humanoid robot platforms and integrated perception, policy inference, and control for real-world execution.
    \item Developed manipulation capabilities for representative laboratory instruments and containers in automated bio-lab scenarios.
    \item Conducted iterative real-robot evaluation and failure analysis to improve deployment robustness.
  \end{itemize}
\end{itemize}

\entry{Beijing Academy of Artificial Intelligence}{Jun. 2025 -- Nov. 2025}{Research Intern (Data Pipeline), Embodied Multimodal Large Models Research Center}{Beijing}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{\textbf{Topic:} Pretraining Data Pipelines for Vision-Language-Action and Vision-Language Models.}
  \begin{itemize}[leftmargin=1.4em, topsep=0.15em, itemsep=0.12em]
    \item Processed large-scale embodied datasets including \textit{AgiBot-World} and \textit{DROID} for VLA pretraining.
    \item Performed action normalization, action tokenization, and dataset reorganization into structured \texttt{JSON} training format.
    \item Standardized multimodal trajectory data for compatibility with large-scale VLA pretraining pipelines.
    \item Contributed to VLM data preprocessing by adding grounding boxes as object-aware visual-language supervision.
  \end{itemize}
\end{itemize}

\section*{Selected Course Projects}

% \entry{RL-based Locomotion Control for Unitree G1}{Mar. 2026 -- Present}{Humanoid Reinforcement Learning}{Project Lead}
% \begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
%   \cvitem{Building on existing humanoid locomotion frameworks, training and adapting reinforcement learning policies for task-specific behaviors on Unitree G1.}
%   \cvitem{Gaining hands-on experience with reinforcement learning, Isaac Sim-based training, and real-robot deployment for humanoid control.}
% \end{itemize}

\entry{Raspberry Pi-based Robotic Arm Control}{Nov. 2025 -- Jan. 2026}{Embedded Systems / Robotics}{Project Lead}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{Developed a Raspberry Pi-based control system for a 3D-printed robotic arm, using GPIO PWM signals to actuate an SG52 servo for gripper control and four-phase eight-step drive signals for 4-phase 5-wire stepper motors at the arm joints.}
  \cvitem{Implemented two interaction modes: infrared remote control via \texttt{lirc} and camera-based gesture control using MediaPipe for real-time arm manipulation.}
\end{itemize}

\entry{Desktop Manipulation via 3D Diffusion Policy}{Mar. 2025 -- Jun. 2025}{Robot Learning / 3D Vision}{Project Lead}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{Built and deployed a real-world 3D Diffusion Policy (DP3) pipeline for tabletop manipulation, including multimodal data collection, camera calibration, point-cloud preprocessing, policy training, and online inference.}
  \cvitem{Validated the system on real tasks including lemon-in-bowl placement, bowl lifting, and drawer pushing using point-cloud observations from a RealSense D435 and an ARX X5 robotic arm.}
\end{itemize}

% \entry{2048 Game System}{Apr. 2024 -- Jun. 2024}{Java / Software Development}{Project Lead}
% \begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
%   \cvitem{Independently built a Java-based 2048 game from scratch, covering GUI frontend design, backend logic implementation, and persistent user data management.}
%   \cvitem{Implemented core modules including account login/registration, save/load, game restart, multiple gameplay modes, and keyboard/button-based control.}
% \end{itemize}

\section*{Leadership and Service}

\entry{Class Leader, Class 2303}{2024 -- 2025}{Class Committee}{}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{Led class operations and activities, including event planning, logistics coordination, routine administration, and award application materials; the class received honors including \textit{Excellent Undergraduate Academic Style}, \textit{Best Sports Team}, and \textit{Best Popularity Class}.}
\end{itemize}

\entry{House Division Lead, Street Dance Club}{2024 -- 2025}{Student Organization}{}
\begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
  \cvitem{Led the House division by coordinating weekly training with instructors and organizing two campus street dance performances, including rehearsal planning and member coordination.}
\end{itemize}

% \section*{Honors and Awards}
% \begin{itemize}[leftmargin=1.2em, topsep=0.2em, itemsep=0.18em]
%   \cvitem{Class-level and university honors through collective leadership contributions, including Excellent Undergraduate Academic Style and Five Four Red Flag Youth League.}
%   \cvitem{Add your personal scholarships, competition awards, paper recognitions, or ranking-based honors here.}
% \end{itemize}

% \section*{Technical Skills}
% \begin{tabularx}{\textwidth}{@{}p{0.18\textwidth}X@{}}
% Programming & Python, C/C++, MATLAB, LaTeX, Linux, Git \\
% Robotics / AI & PyTorch, reinforcement learning basics, literature review, experiment design, technical writing \\
% Languages & Chinese (native), English (working proficiency) \\
% \end{tabularx}

\vspace{0.6em}
% {\footnotesize\color{textgray}Note: This is a sample academic CV drafted to match the clean, traditional style you liked. Replace placeholders (email, GPA, advisor, awards, links) with your exact information before sending it to faculty members.}

\end{document}
